---
title: "Stat 133 Workout 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}
#library(xm12)
library(rvest)
library(dplyr)
library(stringr)
library(ggplot2)
```

### 1) Extract simple information of the authors

```{r}
scholar1 <- "https://scholar.google.com/citations?user="

# For Richard Thaler
author1 <- "Tvzd5GgAAAAJ"
author1_url <- paste0(scholar1, author1)
download.file(author1_url, 'richard_thaler.html')
#richard_thaler <- read_html('richard_thaler.html')
richard_thaler <- read_html('richard_thaler_Scholar.html')

#For Angus Deaton
author2 <- "rvFjcQIAAAAJ"
author2_url <- paste0(scholar1, author2)
download.file(author2_url, 'angus_deaton.html')
angus_deaton <- read_html('angus_deaton.html')
```

Extracting "Richard Thaler":

```{r}
title_RT_html <- html_nodes(richard_thaler, "div#gsc_prf_in")
title_RT <- html_text(title_RT_html)
title_RT
```

Extracting "Angus Deaton":

```{r}
title_AD_html <- html_nodes(angus_deaton, "div#gsc_prf_in")
title_AD <- html_text(title_AD_html)
title_AD
```

Extracting Thaler's associated institution:

```{r}
inst_RT_html <- html_nodes(richard_thaler, "div.gsc_prf_il")
inst_RT <- html_text(inst_RT_html)[1]
inst_RT
```

Extracting Deaton's associated institution:

```{r}
inst_AD_html <- html_nodes(angus_deaton, "div.gsc_prf_il")
inst_AD <- html_text(inst_AD_html)[1]
inst_AD
```

### Question 2 in clean-data-script.R

### 3) Practice with Regular Expressions

a) For the two scholars, how many of their paper titles begin with a word that starts with a vowel, respectively?
```{r}
# Counting for Thaler
thaler_info <- richard_thaler %>% html_nodes(xpath ='//*[@id="gsc_a_b"]') %>% 
  html_nodes(xpath ='tr') %>% html_nodes(xpath ='td') 
step1 = sapply(html_children(thaler_info), html_text)
step1 = step1[step1 != '*']

thaler_df = data.frame(paperName = step1[seq(1, length(step1), 5)],
                        researcher = step1[seq(2, length(step1), 5)],
                        journal = step1[seq(3, length(step1), 5)],
                        citations = step1[seq(4, length(step1), 5)],
                        year = step1[seq(5, length(step1), 5)])
thalerCount <- 0
titles <- thaler_df$paperName
vowels <- c('A','E','I','O','U')
for (i in titles) {
  if (substr(i, 1, 1) == vowels[1]) {
    thalerCount <- thalerCount + 1
  } else if (substr(i, 1, 1) == vowels[2]) {
    thalerCount <- thalerCount + 1
  } else if (substr(i, 1, 1) == vowels[3]) {
    thalerCount <- thalerCount + 1
  } else if (substr(i, 1, 1) == vowels[4]) {
    thalerCount <- thalerCount + 1
  } else if (substr(i, 1, 1) == vowels[5]) {
    thalerCount <- thalerCount + 1
  }
}

# Counting for Deaton
deaton_info <- angus_deaton %>% html_nodes(xpath ='//*[@id="gsc_a_b"]') %>% 
  html_nodes(xpath ='tr') %>% html_nodes(xpath ='td') 
step2 = sapply(html_children(deaton_info), html_text)
step2 = step2[step2 != '*']

deaton_df = data.frame(paperName = step2[seq(1, length(step2), 5)],
                       researcher = step2[seq(2, length(step2), 5)],
                       journal = step2[seq(3, length(step2), 5)],
                       citations = step2[seq(4, length(step2), 5)],
                       year = step2[seq(5, length(step2), 5)])

deatonCount <- 0
for (i in deaton_df$paperName) {
  if (substr(i, 1, 1) == vowels[1]) {
    deatonCount <- deatonCount + 1
  } else if (substr(i, 1, 1) == vowels[2]) {
    deatonCount <- deatonCount + 1
  } else if (substr(i, 1, 1) == vowels[3]) {
    deatonCount <- deatonCount + 1
  } else if (substr(i, 1, 1) == vowels[4]) {
    deatonCount <- deatonCount + 1
  } else if (substr(i, 1, 1) == vowels[5]) {
    deatonCount <- deatonCount + 1
  }
}

# Computing total count
c(thalerCount, deatonCount)
```

b) For the two scholars, how many of their paper titles end with "s" respectively?

```{r}
thalerCountS <- 0
for (i in thaler_df$paperName) {
  if (substr(i, nchar(i), nchar(i)) == 's') {
    thalerCountS <- thalerCountS + 1
  } else if (substr(i, nchar(i), nchar(1)) == 's') {
    thalerCountS <- thalerCountS + 1
  } else if (substr(i, nchar(i), nchar(1)) == 's') {
    thalerCountS <- thalerCountS + 1
  } else if (substr(i, nchar(i), nchar(1)) == 's') {
    thalerCountS <- thalerCountS + 1
  } else if (substr(i, nchar(i), nchar(1)) == 's') {
    thalerCountS <- thalerCountS + 1
  }
}

# Counting for Deaton
deatonCountS <- 0
for (i in deaton_df$paperName) {
  if (substr(i, nchar(i), nchar(i)) == 's') {
    deatonCountS <- deatonCountS + 1
  } else if (substr(i, nchar(i), nchar(i)) == 's') {
    deatonCountS <- deatonCountS + 1
  } else if (substr(i, nchar(i), nchar(i)) == 's') {
    deatonCountS <- deatonCountS + 1
  } else if (substr(i, nchar(i), nchar(i)) == 's') {
    deatonCountS <- deatonCountS + 1
  } else if (substr(i, nchar(i), nchar(i)) == 's') {
    deatonCountS <- deatonCountS + 1
  }
}

# Computing total count
c(thalerCountS, deatonCountS)
```

c) For the two scholars, find the longest title, respectively ("longest" in terms of number of characters).

```{r}
# Finding Thaler's longest title
ncharsThaler <- c()
for (i in thaler_df$paperName) {
  ncharThaler <- nchar(i)
  ncharsThaler <- c(ncharsThaler, ncharThaler)
}
thaler_df %>%
  mutate(num_chars = ncharsThaler) %>%
  filter(num_chars == max(num_chars)) %>%
  select(paperName)
```

```{r}
# Finding Deaton's longest title
ncharsDeaton <- c()
for (i in deaton_df$paperName) {
  ncharDeaton <- nchar(i)
  ncharsDeaton <- c(ncharsDeaton, ncharDeaton)
}
deaton_df %>%
  mutate(num_chars = ncharsDeaton) %>%
  filter(num_chars == max(num_chars)) %>%
  select(paperName)
```

d) For the two scholars, calculate the variable "number of punctuation symbols in the their titles". Display summary() statistics of these variables, and the corresponding histograms.

```{r}
# Calculating for Thaler
thaler_titles <- thaler_df$paperName
thaler_periods <- str_count(thaler_titles, '.')
thaler_commas <- str_count(thaler_titles, ',')
thaler_apostrophe <- str_count(thaler_titles, "''")
#thaler_questions <- str_count(thaler_titles, "?")
thaler_exclaims <- str_count(thaler_titles, "!")
thaler_hyphens <- str_count(thaler_titles, "-")
thalerPunc_df <- data.frame(periods = thaler_periods, commas = thaler_commas, apostrophes = thaler_apostrophe, exclamations = thaler_exclaims, hyphens = thaler_hyphens)
summary(thalerPunc_df)
```

I will now plot some histograms of the various (relevant) data.

```{r}
ggplot(thalerPunc_df, aes(x = periods)) + geom_histogram(color = 'black')
```

```{r}
ggplot(thalerPunc_df, aes(x = commas)) + geom_histogram(color = 'black', fill = 'green')
```

I will now repeat for Deaton.

```{r}
# Calculating for Deaton
deaton_titles <- deaton_df$paperName
deaton_periods <- str_count(deaton_titles, '.')
deaton_commas <- str_count(deaton_titles, ',')
deaton_apostrophe <- str_count(deaton_titles, "''")
#thaler_questions <- str_count(thaler_titles, "?")
deaton_exclaims <- str_count(deaton_titles, "!")
deaton_hyphens <- str_count(deaton_titles, "-")
deatonPunc_df <- data.frame(periods = deaton_periods, commas = deaton_commas, apostrophes = deaton_apostrophe, exclamations = deaton_exclaims, hyphens = deaton_hyphens)
summary(deatonPunc_df)
```

```{r}
ggplot(deatonPunc_df, aes(x = periods)) + geom_histogram(color = 'black', fill = 'green')
```

```{r}
ggplot(thalerPunc_df, aes(x = commas)) + geom_histogram(color = 'black', fill = 'red')
```

e) Remove stop words ("the", "a", "an", "and", "in", "if", "but"), numbers and punctuations from the titles.

```{r}
# For Thaler
words <- c("the", "a", "an", "and", "in", "if", "but", " the ")
thalerRemoved <- str_remove(thaler_titles, words) 
stored_thaler <- c()
for (string in thalerRemoved) {
  splitted <- strsplit(string, " ")
  stored_thaler <- c(stored_thaler, splitted)
}
#table(stored_thaler)
```






























